Volatility and the Buyback Anomaly: Interactive Tool

### 2016-05-08 index.Rmd
shiny simplification

---
title: "Share Buyback and Equity Issue Anomalies Revisited: Interactive Tool"
author: "[Theodoros Evgeniou](http://faculty.insead.edu/theodoros-evgeniou/), [Enric Junqué de Fortuny](http://ciri.be/), [Nick Nassuphis](https://www.linkedin.com/in/nick-nassuphis-8029372), and [Theo Vermaelen](http://faculty.insead.edu/theo-vermaelen/)"
output:  
 html_document:
 fig_width: 6
 fig_height: 2.5
 fig_align: center
 in_header: header.html
 runtime: shiny
runtime: shiny
---

```{r, eval=TRUE, echo = FALSE,message=FALSE}
# rm(list=ls()) # Clean up the memory, if we want to rerun from scratch
# source("create_tool_data.R")
load("bb_issuersTOOL.Rdata")
#load("tmpfiles/bb_issuersALL.Rdata")

@@

  library("stringr")
  library("RcppArmadillo")
  library("gtools")
  library("timeDate")
  library("dygraphs")
  library("reshape")
  library("ggplot2")
}
source("lib/lib_helpers_shiny.R")
source("lib/Paper_global_parameters.R")
source("lib/heatmapOutput.R") 
source("lib/plots.R")
source("report_helpers.R")

DATASET_INI = BUYBACK_DATA$DATASET
DATASET_INI$SDC = as.data.frame(DATASET_INI$SDC)

#if(1) {
#  CACHE <- car_table_cache(DATASET_INI$returns_by_event_monthly,
#                           DATASET_INI$SDC$Event.Date,Risk_Factors_Monthly,formula_used = five_factor_model)
#  save("CACHE",file = "cache.Rdata")
#} else {
#  load("cache.Rdata")  
#}
report_months_cal = c(as.numeric(reported_times[1:(length(reported_times)-1)]),1)
```

@@

```{r, fig.width=6, fig.height=5,echo=FALSE}
shinyApp(
  ui = fluidPage(
    fluidRow(
      column(2,
        conditionalPanel(
          condition = "!$('makeReport').hasClass('shiny-busy')",
          actionButton("makeReport","Generate Report",icon=icon("file"))
        )
      ),
      column(4,
      conditionalPanel(
        condition = "!$('makeReport').hasClass('shiny-busy')",
        uiOutput("downloadButton")
        #downloadButton("downloadReport", "Download Report")
      )
      )
    ),
    busyIndicator("Please wait while we prepare the report ...",wait = 0)
  ),
  server = function(input, output) {
    output$download_button <- renderUI({
        downloadButton("downloadReport", "Download Results")
     })
    makeReportAction <- eventReactive(input$makeReport, {
      #Create the pdf here
      #Sys.sleep(1);return()
      #first check if we didn't already create a paper with these parameters, if so, load from cache
      #filename <- paste("reports/")
      #file.exists()
      tosave= list("startdate","enddate","market_cap_min","market_cap_max","quantile_used_ind","quantile_used_all","characteristic_irats1","characteristic_irats2","characteristic_irats3","characteristic_irats4","characteristic_irats5","characteristic_irats6","characteristic_irats1_sign","characteristic_irats2_sign","characteristic_irats3_sign","characteristic_irats4_sign","characteristic_irats5_sign","characteristic_irats6_sign")
        newinput <- list()
        for(i in tosave) {
          newinput[[i]] <- input[[i]]
        }
        #save("newinput",file=normalizePath("input.Rdata"))
        knitr::knit2pdf("report.Rnw",envir=globalenv())
    })
    output$downloadButton <- renderUI({
      makeReportAction() #only appear after first click on generate
      downloadButton("downloadReport", "Download Report")
    })
    output$downloadReport <- downloadHandler(
      filename = "report.pdf",
      content = function(file) {
        cat(paste("Does the pdf exist?",file.exists("report.pdf")))
        file.rename(normalizePath('report.pdf'), file)
      }
    )
  },
  options = list(height = 120,width=800)
)

@@

```{r, eval=TRUE, echo = FALSE}
dateInput("startdate", "Starting Date:", 
          value = min(DATASET_INI$SDC$Event.Date) - 10, min = min(DATASET_INI$SDC$Event.Date), max = max(DATASET_INI$SDC$Event.Date)-3*370,
          startview = "year",
          width='100%')
```
<br>
```{r, eval=TRUE, echo = FALSE}
dateInput("enddate", "End Date (allow at least 3 years from the starting day you selected - else it will automatically use data up to 3 years after your start date):", 
          value = max(DATASET_INI$SDC$Event.Date) + 10, 
          min = min(DATASET_INI$SDC$Event.Date)+3*370, 
          max = max(DATASET_INI$SDC$Event.Date)+10,startview = "year",
          width='100%')
```

@@

```{r, eval=TRUE, echo = FALSE}
selectInput("market_cap_min","Enter the Minimum Market Cap allowed (in millions):", choices = as.character(c(0,50*(1:20), 500*(1:20))), selected = "0", width = "1000px")
```
<br>
```{r, eval=TRUE, echo = FALSE}
selectInput("market_cap_max","Enter the Maximum Market Cap allowed (in millions):", choices = as.character(c(0,50*(1:20), 500*(1:20), ceiling(max(DATASET_INI$SDC$Market.Cap)))), selected = as.character(ceiling(max(DATASET_INI$SDC$Market.Cap))), width = "1000px")
```

@@

  market_cap_min = as.numeric(input$market_cap_min)
  market_cap_max = as.numeric(input$market_cap_max)
  if (market_cap_max < market_cap_min)
    market_cap_max = ceiling(max(DATASET_INI$SDC$Market.Cap))

  useonly_report = which(DATASET_INI$SDC$Event.Date >= starting & DATASET_INI$SDC$Event.Date <= ending & scrub(DATASET_INI$SDC$Market.Cap) >= market_cap_min & scrub(DATASET_INI$SDC$Market.Cap) <= market_cap_max)

  SDC = DATASET_INI$SDC[useonly_report,]
  returns_by_event_monthly = DATASET_INI$returns_by_event_monthly[,useonly_report]
  DatesMonth = DATASET_INI$DatesMonth[,useonly_report]

  CACHE <- car_table_cache(returns_by_event_monthly,
                         SDC$Event.Date,Risk_Factors_Monthly,formula_used = five_factor_model)

  list(
    CACHE = CACHE,
    returns_by_event_monthly = returns_by_event_monthly,
    DatesMonth = DatesMonth,
    SDC = SDC,
    subset = useonly_report
    #returns_by_event_monthly = DATASET_INI$returns_by_event_monthly,
    #DatesMonth = DATASET_INI$DatesMonth,
    #SDC = DATASET_INI$SDC
  )
})

@@

```{r, eval=TRUE, echo = FALSE}
acceptaple_features = c("Prior.Returns.Score", "BE.ME.Score","Size.Score" ,"Valuation.Index", "Market.Cap",          "Percent.Shares","Market.beta","SMB.beta","HML.beta" , "RMW.beta" ,"CMA.beta", "one.minus.Rsq.Score", "pre.vol.Score","ivol", "leverage.ratio","Industry", "Purpose.Code","Source.of.funds")

fluidPage(
  selectInput("characteristic", "Select Firm Characteristic:", choices = acceptaple_features,selected = acceptaple_features[4]),
  mainPanel(
    tabsetPanel("Example",
                tabPanel("Histogram",
                         busyIndicator("Please wait while we load the data for you... This shouldn't take more than a few seconds...",wait = 0),
                         renderPlot({
                           feature = DATASET_NEW()$SDC[[which(names(DATASET_NEW()$SDC) == input$characteristic)]]
                           feature = feature[!is.na(feature)]
                           if (!is.numeric(feature))
                             feature = 1
                           hist(feature, density = 100, breaks = 100)
                         })),
                tabPanel("Summary Statistics",
                         renderDataTable({
                           feature = DATASET_NEW()$SDC[[which(names(DATASET_NEW()$SDC) == input$characteristic)]]
                           #feature = feature[!is.na(feature)]
                           if (length(unique(feature)) > 20 & is.numeric(feature)){
                             res = t(as.matrix(summary(feature)))
                             colnames(res) <- c("Minimum", "1st Quantile", "Median", "Mean", "3rd Quantile", "Max")
                           }
                           if (is.character(feature) | length(unique(feature)) <= 20){
                             tmp = sort(table(feature), decreasing = TRUE)
                             res = t(as.matrix(tmp))
                           }
                           as.data.frame(res)
                           #m1<-gvisTable(show_data,options=list(showRowNumber=TRUE,width=1220, height=min(400,27*(nrow(show_data)+1)),allowHTML=TRUE,page='disable'))
                           #print(m1,'chart')
                         })
                )
    ),
    style='width: 100%;'))
```

@@

```{r, eval=TRUE, echo = FALSE}
checkboxGroupInput("industry", "Select Industries to remove:", choices = unique(DATASET_INI$SDC$Industry),selected = NULL,inline=TRUE)

@@

feature_IRATStable_industry <- reactive({
  useonly_industry = !(DATASET_NEW()$SDC$Industry %in% input$industry) 
  #cat(paste("Total left after filtering industry:",sum(useonly_industry)))
  #instead of using company_subset_undervalued and _overvalued, use Valuation Index
  thefeature = DATASET_NEW()$SDC[[which(names(DATASET_NEW()$SDC) == "Valuation.Index")]]
  thefeature = as.numeric(scrub(thefeature))
  quantile_used_ind = as.numeric(0.2)
  High_feature_events = !is.na(thefeature) & scrub(thefeature) >= quantile(scrub(thefeature[!is.na(thefeature)]),1-quantile_used_ind)
  Low_feature_events  = !is.na(thefeature) & scrub(thefeature) <= quantile(scrub(thefeature[!is.na(thefeature)]),quantile_used_ind)

  res = round(cbind(
    #car_table_cached(DATASET_NEW()$CACHE,useonly_industry & DATASET_NEW()$SDC$company_subset_overvalued)$results,
    #car_table_cached(DATASET_NEW()$CACHE,useonly_industry & DATASET_NEW()$SDC$company_subset_undervalued)$results
    car_table_cached(DATASET_NEW()$CACHE,useonly_industry & Low_feature_events)$results,
    car_table_cached(DATASET_NEW()$CACHE,useonly_industry & High_feature_events)$results
  ),2)[reported_times,]
  colnames(res) <- c("Low: CAR", "t-stat","p-value", "High: CAR", "t-stat","p-value")
  as.data.frame(res)
})

feature_CALtable_industry <- reactive({
    thefeature = DATASET_NEW()$SDC[[which(names(DATASET_NEW()$SDC) == "Valuation.Index")]]
  thefeature = as.numeric(scrub(thefeature))
  quantile_used_ind = as.numeric(0.2)
  High_feature_events = !is.na(thefeature) & scrub(thefeature) >= quantile(scrub(thefeature[!is.na(thefeature)]),1-quantile_used_ind)
  Low_feature_events  = !is.na(thefeature) & scrub(thefeature) <= quantile(scrub(thefeature[!is.na(thefeature)]),quantile_used_ind)

  useonly_industry = !(DATASET_NEW()$SDC$Industry %in% input$industry) 
  res = round(cbind(
    #calendar_table2(DATASET_NEW()$returns_by_event_monthly[,useonly_industry & DATASET_NEW()$SDC$company_subset_overvalued], DATASET_NEW()$SDC$Event.Date[useonly_industry & DATASET_NEW()$SDC$company_subset_overvalued], Risk_Factors_Monthly,report_months_cal)$results,
    #calendar_table2(DATASET_NEW()$returns_by_event_monthly[,useonly_industry & DATASET_NEW()$SDC$company_subset_undervalued], DATASET_NEW()$SDC$Event.Date[useonly_industry& DATASET_NEW()$SDC$company_subset_undervalued], Risk_Factors_Monthly,report_months_cal)$results
    calendar_table2(DATASET_NEW()$returns_by_event_monthly[,useonly_industry & Low_feature_events], DATASET_NEW()$SDC$Event.Date[useonly_industry& Low_feature_events], Risk_Factors_Monthly,report_months_cal)$results,
        calendar_table2(DATASET_NEW()$returns_by_event_monthly[,useonly_industry & High_feature_events], DATASET_NEW()$SDC$Event.Date[useonly_industry & High_feature_events], Risk_Factors_Monthly,report_months_cal)$results

  ),2)[reported_times,]
  colnames(res) <- c("Low: CAL", "t-stat","p-value", "High: CAL", "t-stat","p-value")
  as.data.frame(res)
})

@@

```{r, eval=TRUE, echo = FALSE}
acceptaple_features1 = c("Prior.Returns.Score", "BE.ME.Score","Size.Score" ,"Valuation.Index", "Market.Cap",          "Percent.Shares", "Market.beta","SMB.beta","HML.beta" , "RMW.beta" ,"CMA.beta", "one.minus.Rsq.Score", "pre.vol.Score","ivol", "leverage.ratio")

selectInput("characteristic_irats", "Select Firm Characteristic to Define High/Low Firms:", choices = acceptaple_features1,selected = acceptaple_features1[4], width = "1000px")

@@

feature_IRATStable <- reactive({
  thesign = ifelse(input$characteristic_irats_sign, -1, +1)
  thefeature = thesign*DATASET_NEW()$SDC[[which(names(DATASET_NEW()$SDC) == input$characteristic_irats)]]

@@

  #High_feature_events = which(scrub(thefeature) > quantile(thefeature[!is.na(thefeature)],1-as.numeric(input$quantile_used)) & !is.na(thefeature))
  #Low_feature_events = which(scrub(thefeature) < quantile(thefeature[!is.na(thefeature)],as.numeric(input$quantile_used)) & !is.na(thefeature))
  res = round(cbind(
    #car_table(DATASET_NEW()$returns_by_event_monthly[,Low_feature_events], DATASET_NEW()$SDC$Event.Date[Low_feature_events], Risk_Factors_Monthly)$results,
    #car_table(DATASET_NEW()$returns_by_event_monthly[,High_feature_events], DATASET_NEW()$SDC$Event.Date[High_feature_events], Risk_Factors_Monthly)$results
    car_table_cached(DATASET_NEW()$CACHE,Low_feature_events)$results,
    car_table_cached(DATASET_NEW()$CACHE,High_feature_events)$results
  ),2)[reported_times,]
  colnames(res) <- c("Low: CAR", "t-stat","p-value", "High: CAR", "t-stat","p-value")
  as.data.frame(res)
})

feature_CALtable <- reactive({
  thesign = ifelse(input$characteristic_irats_sign, -1, +1)
  thefeature = thesign*DATASET_NEW()$SDC[[which(names(DATASET_NEW()$SDC) == input$characteristic_irats)]]  
  High_feature_events = which(scrub(thefeature) > quantile(thefeature[!is.na(thefeature)],1-as.numeric(input$quantile_used)) & !is.na(thefeature))
  Low_feature_events = which(scrub(thefeature) < quantile(thefeature[!is.na(thefeature)],as.numeric(input$quantile_used)) & !is.na(thefeature))
  res = round(cbind(
    calendar_table2(DATASET_NEW()$returns_by_event_monthly[,Low_feature_events], DATASET_NEW()$SDC$Event.Date[Low_feature_events], Risk_Factors_Monthly,report_months_cal)$results,
    calendar_table2(DATASET_NEW()$returns_by_event_monthly[,High_feature_events], DATASET_NEW()$SDC$Event.Date[High_feature_events], Risk_Factors_Monthly,report_months_cal)$results
  ),2)[reported_times,]
  colnames(res) <- c("Low: CAL", "t-stat","p-value", "High: CAL", "t-stat","p-value")
  as.data.frame(res)
})

High_feature_Hedged_react <- reactive({
  thefeature = as.numeric(DATASET_NEW()$SDC[[which(names(DATASET_NEW()$SDC) == input$characteristic_irats)]])
  quantile_used <- as.numeric(input$quantile_used)

@@

Low_feature_Hedged_react <- reactive({
  thefeature = DATASET_NEW()$SDC[[which(names(DATASET_NEW()$SDC) == input$characteristic_irats)]]  
  Low_feature_events = which(scrub(thefeature) < quantile(thefeature[!is.na(thefeature)],as.numeric(input$quantile_used)) & !is.na(thefeature))
  Low_feature <- apply(PNL_matrix_BB(start_date_event,"One.Year.After", Low_feature_events,  DATASET_NEW()$DatesMonth, DATASET_NEW()$returns_by_event_monthly,event=1),1,non_zero_mean)
  remove_initialization_time(suppressWarnings(scrub(alpha_lm(Low_feature,Risk_Factors_Monthly[,pnl_hedge_factors],hedge_months,trade=1))),min_date=FirstTrade)  
})

@@

```{r, eval=TRUE, echo = FALSE}
acceptaple_features2 = c("Prior.Returns.Score", "BE.ME.Score","Size.Score" ,"Valuation.Index", "Market.Cap",          "Percent.Shares", "Market.beta","SMB.beta","HML.beta" , "RMW.beta" ,"CMA.beta", "one.minus.Rsq.Score", "pre.vol.Score","ivol", "leverage.ratio","None")
```

<br>
```{r, eval=TRUE, echo = FALSE}
fluidPage( 
  h4("Firm Characteristics of the new index"),
  fluidRow(
    column(6,
      selectInput("characteristic_irats1", "First Firm Characteristic:", choices = acceptaple_features2,selected = acceptaple_features2[4], width = "425px"),
      checkboxInput("characteristic_irats1_sign", "Reverse", value = FALSE),
      selectInput("characteristic_irats2", "Second Firm Characteristic:", choices = acceptaple_features2,selected ="None", width = "425px"),
checkboxInput("characteristic_irats2_sign", "Reverse", value = FALSE),
    selectInput("characteristic_irats3", "Third Firm Characteristic:", choices = acceptaple_features2,selected = "None", width = "425px"),
checkboxInput("characteristic_irats3_sign", "Reverse", value = FALSE)
     ),
  column(6,
      selectInput("characteristic_irats4", "Fourth Firm Characteristic:", choices = acceptaple_features2,selected = "None", width = "425px"),
      checkboxInput("characteristic_irats4_sign", "Reverse", value = FALSE),
    selectInput("characteristic_irats5", "Fifth Firm Characteristic:", choices = acceptaple_features2,selected = "None", width = "425px"),
    checkboxInput("characteristic_irats5_sign", "Reverse", value = FALSE),
    selectInput("characteristic_irats6", "Sixth Firm Characteristic:", choices = acceptaple_features2,selected = "None", width = "425px"),
    checkboxInput("characteristic_irats6_sign", "Reverse", value = FALSE)
    )
  )
)
```

@@

  thesign = ifelse(input$characteristic_irats1_sign, -1, +1)
  thefeature = thesign*DATASET_NEW()$SDC[[which(names(DATASET_NEW()$SDC) == input$characteristic_irats1)]]  
  High_feature_events1 = (scrub(thefeature) >= quantile(thefeature[!is.na(thefeature)],1-as.numeric(input$quantile_used_ind)) & !is.na(thefeature))
  Low_feature_events1 = (scrub(thefeature) <= quantile(thefeature[!is.na(thefeature)],as.numeric(input$quantile_used_ind)) & !is.na(thefeature))

  High_feature_events2 <- High_feature_events3 <- High_feature_events4 <- High_feature_events5 <- High_feature_events6 <- rep(FALSE,length(High_feature_events1))
  Low_feature_events2 <- Low_feature_events3 <- Low_feature_events4 <- Low_feature_events5 <- Low_feature_events6 <- 
    rep(FALSE,length(Low_feature_events1))

>>>>

---
title: "Volatility and the Buyback Anomaly: Interactive Tool"
author: "[Theodoros Evgeniou](http://faculty.insead.edu/theodoros-evgeniou/), [Enric Junqué de Fortuny](http://ciri.be/), [Nick Nassuphis](https://www.linkedin.com/in/nick-nassuphis-8029372), and [Theo Vermaelen](http://faculty.insead.edu/theo-vermaelen/)"
output:  
 html_document:
 fig_width: 6
 fig_height: 2.5
 fig_align: center
 in_header: header.html
 runtime: shiny
runtime: shiny
---

```{r, eval=TRUE, echo = FALSE,message=FALSE}
# rm(list=ls()) # Clean up the memory, if we want to rerun from scratch
load("bb_issuersTOOL.Rdata")

@@

  library("stringr")
  library("RcppArmadillo")
  library("gtools")
  library("timeDate")
  library("dygraphs")
  library("reshape")
  library("ggplot2")
}

source("../FinanceLibraries/lib_helpers.R", chdir=TRUE)
source("../FinanceLibraries/latex_code.R")
source("../FinanceData/rawdata_fama_french/ff_industries_sic.R")
source("Paper_global_parameters.R")
source("../FinanceLibraries/heatmapOutput.R") 
source("../FinanceLibraries/shiny_plots.R")

report_months_cal = c(as.numeric(reported_times[1:(length(reported_times)-1)]),1)
BUYBACK_DATA_TOOL$None <- 1:length(BUYBACK_DATA_TOOL$Prior.Returns.Score)

value.weights = rep(1,length(BUYBACK_DATA_TOOL$Prior.Returns.Score))
acceptaple_features = setdiff(names(BUYBACK_DATA_TOOL),c("Event.Date", "Industry_name","Event.Size"))
```

@@

```{r, fig.width=6, fig.height=5,echo=FALSE}
shinyApp(
  ui = fluidPage(
    fluidRow(
      column(2,
             conditionalPanel(
               condition = "!$('makeReport').hasClass('shiny-busy')",
               actionButton("makeReport","Generate Report (Work in Progress)",icon=icon("file"))
             )
      ),
      column(4,
             conditionalPanel(
               condition = "!$('makeReport').hasClass('shiny-busy')",
               uiOutput("downloadButton")
               #downloadButton("downloadReport", "Download Report")
             )
      )
    ),
    busyIndicator("Please wait while we prepare the report ...",wait = 0)
  ),
  server = function(input, output) {
    output$download_button <- renderUI({
      downloadButton("downloadReport", "Download Results")
    })
    makeReportAction <- eventReactive(input$makeReport, {
      #Create the pdf here
      #Sys.sleep(1);return()
      #first check if we didn't already create a paper with these parameters, if so, load from cache
      #filename <- paste("reports/")
      #file.exists()
      tosave= list("startdate","enddate","market_cap_min","market_cap_max","quantile_used_ind","quantile_used_all","characteristic_irats1","characteristic_irats2","characteristic_irats3","characteristic_irats4","characteristic_irats5","characteristic_irats6","characteristic_irats1_sign","characteristic_irats2_sign","characteristic_irats3_sign","characteristic_irats4_sign","characteristic_irats5_sign","characteristic_irats6_sign")
      newinput <- list()
      for(i in tosave) {
        newinput[[i]] <- input[[i]]
      }
      # Not yet available
      #knitr::knit2pdf("report.Rnw",envir=globalenv())
    })
    output$downloadButton <- renderUI({
      makeReportAction() #only appear after first click on generate
      downloadButton("downloadReport", "Download Report")
    })
    output$downloadReport <- downloadHandler(
      filename = "report.pdf",
      content = function(file) {
        cat(paste("Does the pdf exist?",file.exists("report.pdf")))
        file.rename(normalizePath('report.pdf'), file)
      }
    )
  },
  options = list(height = 120,width=800)
)

@@

```{r, eval=TRUE, echo = FALSE}
dateInput("startdate", "Starting Date:", 
          value = min(BUYBACK_DATA_TOOL$Event.Date) - 10, min = min(BUYBACK_DATA_TOOL$Event.Date), max = max(BUYBACK_DATA_TOOL$Event.Date)-3*370,
          startview = "year",
          width='100%')
```
<br>
```{r, eval=TRUE, echo = FALSE}
dateInput("enddate", "End Date (allow at least 3 years from the starting day you selected - else it will automatically use data up to 3 years after your start date):", 
          value = max(BUYBACK_DATA_TOOL$Event.Date) + 10, 
          min = min(BUYBACK_DATA_TOOL$Event.Date)+3*370, 
          max = max(BUYBACK_DATA_TOOL$Event.Date)+10,startview = "year",
          width='100%')
```

@@

```{r, eval=TRUE, echo = FALSE}
selectInput("market_cap_min","Enter the Minimum Market Cap allowed (in millions):", choices = as.character(c(0,50*(1:20), 500*(1:20))), selected = "0", width = "1000px")
```
<br>
```{r, eval=TRUE, echo = FALSE}
selectInput("market_cap_max","Enter the Maximum Market Cap allowed (in millions):", choices = as.character(c(0,50*(1:20), 500*(1:20), ceiling(max(BUYBACK_DATA_TOOL$Market.Cap)))), selected = as.character(ceiling(max(BUYBACK_DATA_TOOL$Market.Cap))), width = "1000px")
```

@@

  market_cap_min = as.numeric(input$market_cap_min)
  market_cap_max = as.numeric(input$market_cap_max)
  if (market_cap_max < market_cap_min)
    market_cap_max = ceiling(max(BUYBACK_DATA_TOOL$Market.Cap))

  useonly_report = which(BUYBACK_DATA_TOOL$Event.Date >= starting & BUYBACK_DATA_TOOL$Event.Date <= ending & scrub(BUYBACK_DATA_TOOL$Market.Cap) >= market_cap_min & scrub(BUYBACK_DATA_TOOL$Market.Cap) <= market_cap_max)

  list(
    BUYBACK_DATA_TOOL=BUYBACK_DATA_TOOL[useonly_report,],
    returns_by_event_monthly = returns_by_event_monthly[,useonly_report],
    DatesMonth  = DatesMonth[,useonly_report],
    subset = useonly_report
  )
})

@@

```{r, eval=TRUE, echo = FALSE}
fluidPage(
  selectInput("characteristic", "Select Firm Characteristic:", choices = acceptaple_features,selected = acceptaple_features[4]),
  mainPanel(
    tabsetPanel("Example",
                tabPanel("Histogram",
                         busyIndicator("Please wait while we load the data for you... This shouldn't take more than a few seconds...",wait = 0),
                         renderPlot({
                           feature = DATASET_NEW()$BUYBACK_DATA_TOOL[,which(names(DATASET_NEW()$BUYBACK_DATA_TOOL) == input$characteristic)]
                           feature = feature[!is.na(feature)]
                           if (!is.numeric(feature))
                             feature = 1
                           hist(feature, density = 100, breaks = 100)
                         })),
                tabPanel("Summary Statistics",
                         renderDataTable({
                           feature = DATASET_NEW()$BUYBACK_DATA_TOOL[,which(names(DATASET_NEW()$BUYBACK_DATA_TOOL) == input$characteristic)]
                           feature = feature[!is.na(feature)]
                           if (length(unique(feature)) > 20 & is.numeric(feature)){
                             res = t(as.matrix(summary(feature)))
                             colnames(res) <- c("Minimum", "1st Quantile", "Median", "Mean", "3rd Quantile", "Max")
                           }
                           if (is.character(feature) | length(unique(feature)) <= 20){
                             tmp = sort(table(feature), decreasing = TRUE)
                             res = t(as.matrix(tmp))
                           }
                           as.data.frame(res)
                           #m1<-gvisTable(show_data,options=list(showRowNumber=TRUE,width=1220, height=min(400,27*(nrow(show_data)+1)),allowHTML=TRUE,page='disable'))
                           #print(m1,'chart')
                         })
                )
    ),
    style='width: 100%;'))
```

@@

```{r, eval=TRUE, echo = FALSE}
checkboxGroupInput("industry", "Select Industries to remove:", choices = unique(BUYBACK_DATA_TOOL$Industry_name),selected = NULL,inline=TRUE) 
```
<br>
<br>
```{r, eval=TRUE, echo = FALSE}
selectInput("quantile_used_industry","Enter the quantile to use to define High and Low Firms for this analysis:", choices = 0.02*(1:20), selected = "0.2", width = "1000px")
```

@@

feature_IRATStable_industry <- reactive({
  useonly_industry = !(DATASET_NEW()$BUYBACK_DATA_TOOL$Industry_name %in% input$industry) 
  thefeature = DATASET_NEW()$BUYBACK_DATA_TOOL[[which(names(DATASET_NEW()$BUYBACK_DATA_TOOL) == "Valuation.Index")]]
  #quantile_used_ind = as.numeric(0.2)
  quantile_used_ind = as.numeric(input$quantile_used_industry)

  res = round(cbind(
    car_table(returns_by_event_monthly[,useonly_industry & Low_feature_events],
              BUYBACK_DATA_TOOL$Event.Date[useonly_industry & Low_feature_events],Risk_Factors_Monthly,formula_used = five_factor_model)$results,
    car_table(returns_by_event_monthly[,useonly_industry & High_feature_events],
              BUYBACK_DATA_TOOL$Event.Date[useonly_industry & High_feature_events],Risk_Factors_Monthly,formula_used = five_factor_model)$results
  ),2)[reported_times,]
  colnames(res) <- c("Low: CAR", "t-stat","p-value", "High: CAR", "t-stat","p-value")
  as.data.frame(res)
})

feature_CALtable_industry <- reactive({
  useonly_industry = !(DATASET_NEW()$BUYBACK_DATA_TOOL$Industry_name %in% input$industry) 
  thefeature = DATASET_NEW()$BUYBACK_DATA_TOOL[[which(names(DATASET_NEW()$BUYBACK_DATA_TOOL) == "Valuation.Index")]]
  #quantile_used_ind = as.numeric(0.2)
  quantile_used_ind = as.numeric(input$quantile_used_industry)

  res = round(cbind(
    calendar_table(returns_by_event_monthly[,useonly_industry & Low_feature_events],
                   BUYBACK_DATA_TOOL$Event.Date[useonly_industry & Low_feature_events],Risk_Factors_Monthly,formula_used = five_factor_model, value.weights = value.weights[useonly_industry & Low_feature_events])$results,
    calendar_table(returns_by_event_monthly[,useonly_industry & High_feature_events],
                   BUYBACK_DATA_TOOL$Event.Date[useonly_industry & High_feature_events],Risk_Factors_Monthly,formula_used = five_factor_model, value.weights = value.weights[useonly_industry & Low_feature_events])$results
  ),2)[reported_times,]
  colnames(res) <- c("Low: CAL", "t-stat","p-value", "High: CAL", "t-stat","p-value")
  as.data.frame(res)
})

@@

```{r, eval=TRUE, echo = FALSE}
selectInput("characteristic_irats", "Select Firm Characteristic to Define High/Low Firms:", choices = acceptaple_features,selected = acceptaple_features[4], width = "1000px")

@@

feature_IRATStable <- reactive({
  thesign = ifelse(input$characteristic_irats_sign, -1, +1)
  thefeature = thesign*DATASET_NEW()$BUYBACK_DATA_TOOL[[which(names(DATASET_NEW()$BUYBACK_DATA_TOOL) == input$characteristic_irats)]]

@@

  res = round(cbind(
    car_table(returns_by_event_monthly[, Low_feature_events],
              BUYBACK_DATA_TOOL$Event.Date[ Low_feature_events],Risk_Factors_Monthly,formula_used = five_factor_model)$results,
    car_table(returns_by_event_monthly[, High_feature_events],
              BUYBACK_DATA_TOOL$Event.Date[High_feature_events],Risk_Factors_Monthly,formula_used = five_factor_model)$results
  ),2)[reported_times,]

  colnames(res) <- c("Low: CAR", "t-stat","p-value", "High: CAR", "t-stat","p-value")
  as.data.frame(res)
})

feature_CALtable <- reactive({
  thesign = ifelse(input$characteristic_irats_sign, -1, +1)
  thefeature = thesign*DATASET_NEW()$BUYBACK_DATA_TOOL[[which(names(DATASET_NEW()$BUYBACK_DATA_TOOL) == input$characteristic_irats)]]  
  High_feature_events = which(scrub(thefeature) > quantile(thefeature[!is.na(thefeature)],1-as.numeric(input$quantile_used)) & !is.na(thefeature))
  Low_feature_events = which(scrub(thefeature) < quantile(thefeature[!is.na(thefeature)],as.numeric(input$quantile_used)) & !is.na(thefeature))

  res = round(cbind(
    calendar_table(returns_by_event_monthly[, Low_feature_events],
                   BUYBACK_DATA_TOOL$Event.Date[Low_feature_events],Risk_Factors_Monthly,formula_used = five_factor_model, value.weights = value.weights[Low_feature_events])$results,
    calendar_table(returns_by_event_monthly[,High_feature_events],
                   BUYBACK_DATA_TOOL$Event.Date[High_feature_events],Risk_Factors_Monthly,formula_used = five_factor_model, value.weights = value.weights[High_feature_events])$results
  ),2)[reported_times,]

  colnames(res) <- c("Low: CAL", "t-stat","p-value", "High: CAL", "t-stat","p-value")
  as.data.frame(res)
})

High_feature_Hedged_react <- reactive({
  thefeature = as.numeric(DATASET_NEW()$BUYBACK_DATA_TOOL[[which(names(DATASET_NEW()$BUYBACK_DATA_TOOL) == input$characteristic_irats)]])
  quantile_used <- as.numeric(input$quantile_used)

@@

Low_feature_Hedged_react <- reactive({
  thefeature = DATASET_NEW()$BUYBACK_DATA_TOOL[[which(names(DATASET_NEW()$BUYBACK_DATA_TOOL) == input$characteristic_irats)]]  
  Low_feature_events = which(scrub(thefeature) < quantile(thefeature[!is.na(thefeature)],as.numeric(input$quantile_used)) & !is.na(thefeature))
  Low_feature <- apply(PNL_matrix_BB(start_date_event,"One.Year.After", Low_feature_events,  DATASET_NEW()$DatesMonth, DATASET_NEW()$returns_by_event_monthly,event=1),1,non_zero_mean)
  remove_initialization_time(suppressWarnings(scrub(alpha_lm(Low_feature,Risk_Factors_Monthly[,pnl_hedge_factors],hedge_months,trade=1))),min_date=FirstTrade)  
})

@@

<br>
```{r, eval=TRUE, echo = FALSE}
fluidPage( 
  h4("Firm Characteristics of the new index"),
  fluidRow(
    column(6,
           selectInput("characteristic_irats1", "First Firm Characteristic:", choices = acceptaple_features,selected = acceptaple_features[4], width = "425px"),
           checkboxInput("characteristic_irats1_sign", "Reverse", value = FALSE),
           selectInput("characteristic_irats2", "Second Firm Characteristic:", choices = acceptaple_features,selected ="None", width = "425px"),
           checkboxInput("characteristic_irats2_sign", "Reverse", value = FALSE),
           selectInput("characteristic_irats3", "Third Firm Characteristic:", choices = acceptaple_features,selected = "None", width = "425px"),
           checkboxInput("characteristic_irats3_sign", "Reverse", value = FALSE)
    ),
    column(6,
           selectInput("characteristic_irats4", "Fourth Firm Characteristic:", choices = acceptaple_features,selected = "None", width = "425px"),
           checkboxInput("characteristic_irats4_sign", "Reverse", value = FALSE),
           selectInput("characteristic_irats5", "Fifth Firm Characteristic:", choices = acceptaple_features,selected = "None", width = "425px"),
           checkboxInput("characteristic_irats5_sign", "Reverse", value = FALSE),
           selectInput("characteristic_irats6", "Sixth Firm Characteristic:", choices = acceptaple_features,selected = "None", width = "425px"),
           checkboxInput("characteristic_irats6_sign", "Reverse", value = FALSE)
    )
  )
)
```

@@

  thesign = ifelse(input$characteristic_irats1_sign, -1, +1)
  thefeature1 = (thesign==-1) + thesign*DATASET_NEW()$BUYBACK_DATA_TOOL[[which(names(DATASET_NEW()$BUYBACK_DATA_TOOL) == input$characteristic_irats1)]]  
  High_feature_events1 = (scrub(thefeature1) >= quantile(thefeature1[!is.na(thefeature1)],1-as.numeric(input$quantile_used_ind)) & !is.na(thefeature1))
  Low_feature_events1 = (scrub(thefeature1) <= quantile(thefeature1[!is.na(thefeature1)],as.numeric(input$quantile_used_ind)) & !is.na(thefeature1))

  thefeature2 <- thefeature3 <- thefeature4 <- thefeature5 <- thefeature6 <- rep(0,length(High_feature_events1))
  High_feature_events2 <- High_feature_events3 <- High_feature_events4 <- High_feature_events5 <- High_feature_events6 <- rep(FALSE,length(High_feature_events1))
  Low_feature_events2 <- Low_feature_events3 <- Low_feature_events4 <- Low_feature_events5 <- Low_feature_events6 <- 
    rep(FALSE,length(Low_feature_events1))
